---
title: "Marco Mid-term HW Calibration"
author: "Group2"
date: "2018/12/6"
output:
  pdf_document:
    latex_engine: xelatex
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r set to global enviro}
rho2 <- 0.01035 
delta2 <- 0.04 
tau_k2 <- 0.03  
alpha2 <- 0.64 
sigma2 <- 0.7  
A2 <- 1
epsilon2 <- 0.77 
tau_l2 <- 0.12 
tau_c2 <- 0.05
```

```{r, include=FALSE}
library(readxl)
library(tidyverse)
library(magrittr)
```

### A. Before the Comparative Statics

As we know the l* = 0.3525, then we can solve initial k from the `return` function.
```{r 求解起初k*}
lzero <- 0.3525

funtok <- function(k) {
  return(lzero-(((rho2+delta2*(1-tau_k2))/((1-tau_k2)*(1-alpha2)*A2))^(1/alpha2))*k)

}

uniroot(funtok, c(-3,100), tol = 0.000000001) -> solofk

solofk$root -> kzero

kzero
```

After we get kzero(initial k*), we can solve initial c.
```{r 求解期初c}
funtoc <- function(c) {
  
  return(c-(((rho2+delta2*(1-tau_k2))/((1-tau_k2)*(1-alpha2)))-delta2)*kzero)
}

uniroot(funtoc, c(-3,50), tol = 0.000000001) -> solofc

solofc$root -> czero

czero
```

After getting the initial l* and k*, then we can solve initial y.
```{r 期初y值}
yzero <- A2*(lzero^alpha2)*(kzero^(1-alpha2))
yzero
```

So far, we can get the endogenous variables in the model.
```{r 期初內解變數值, eval=FALSE}
lzero 
kzero 
czero 
yzero 
```

### B. Solve the chi in this model

```{r 求解chi}
funTochi <- function(chi){
    rho2 <- 0.01035 
    delta2 <- 0.04 
    tau_k2 <- 0.03  
    alpha2 <- 0.64 
    sigma2 <- 0.7  
    A2 <- 1 
    epsilon2 <- 0.77 
    tau_l2 <- 0.12 
    tau_c2 <- 0.05
    
    w <- A2*alpha2*(lzero^(alpha2-1))*(kzero^(1-alpha2))
    
M <- ((1-tau_l2)*w)/(chi*(1+tau_c2))

P <- (1-(((rho2+delta2*(1-tau_k2))/((1-tau_k2)*(1-alpha2)*A2))^(1/alpha2))*kzero)
Q <- (((1-tau_k2)*(1-alpha2))/(rho2+alpha2*delta2*(1-tau_k2)))

return(kzero-(((M^(1/sigma2))*(P^(epsilon2/sigma2))*Q)))
}

uniroot(funTochi, c(0,10000), tol = 0.0001, extendInt = "yes") -> solofchi2


chi2 <- solofchi2$root
chi2
```

At the same time, we have initial c and l, so we can slove initial u.
```{r 計算期初u值}
R <- ((czero^(1-sigma2)-1)/(1-sigma2))
S <- chi2*(((1-lzero)^(1-epsilon2))/(1-epsilon2))
uzero <- R+S
uzero
```

Now, we know all we need before the comparative statics.
```{r 期初內解變數值&chi, eval=FALSE}
lzero 
kzero 
czero 
yzero 
chi2 
```

```{r}
c(c("kzero", "lzero", "czero", "yzero", "uzero"), round(c(kzero,lzero,czero,yzero,uzero), digits = 6)) -> Beforestatics
Beforestatics
```

### C. Comparative Statics

tau_k decrease from 0.03 to 0.025
```{r 比較靜態外生參數 tau_k3}

rho3 <- 0.01035 
delta3 <- 0.04 
tau_k3 <- 0.025  
alpha3 <- 0.64 
sigma3 <- 0.7  
A3 <- 1 
epsilon3 <- 0.77 
tau_l3 <- 0.12 
tau_c3 <- 0.05
chi3 <- chi2
```

Solve new k, and we name it *kone1*
```{r 求解新的kone}
funToFindkone <- function(kone){

    l <- (((rho3+delta3*(1-tau_k3))/((1-tau_k3)*(1-alpha3)*A3))^(1/alpha3))*kone
    w <- A3*alpha3*l^(alpha3-1)*kone^(1-alpha3)
    
M <- ((1-tau_l3)*w)/(chi3*(1+tau_c3))

P <- (1-(((rho3+delta3*(1-tau_k3))/((1-tau_k3)*(1-alpha3)*A3))^(1/alpha3))*kone)
Q <- (((1-tau_k3)*(1-alpha3))/(rho3+alpha3*delta3*(1-tau_k3)))

return(kone-(((M^(1/sigma3))*(P^(epsilon3/sigma3))*Q)))
}

uniroot(funToFindkone, c(1,10), tol = 0.000000001) -> solofkone

kone1 <- solofkone$root
kone1
```

After getting k*  (the `kone1`) from comparative statics, we can solve other endogenous variables.
```{r 求解比較靜態後的其他內解變數值}
funoflcone <- function(kvalue) {

  lone <- (((rho3+delta3*(1-tau_k3))/((1-tau_k3)*(1-alpha3)*A3))^(1/alpha3))*kvalue
  cone <- (((rho3+delta3*(1-tau_k3))/((1-tau_k3)*(1-alpha3)))-delta3)*kvalue
  yone <- A3*(lone^alpha3)*(kvalue^(1-alpha3))
  
  R <- ((cone^(1-sigma3)-1)/(1-sigma3))
  S <- chi3*(((1-lone)^(1-epsilon3))/(1-epsilon3))
  uone <- R+S
  
  c(c("kone", "lone", "cone", "yone", "uone"), round(c(kvalue,lone,cone,yone,uone), digits = 6)) -> Afterstatics
  
  Afterstatics
}




funoflcone(kone1)
Beforestatics

```




